\section{Introduction}
\label{sec:intro}

Earnings conference calls are one of the few recurring events at which management
speaks at length, semi-spontaneously, about a public company---in both \emph{what}
is said (the transcript) and \emph{how} it is said (the audio). A line of research
beginning with \citet{qin2019what} and continuing through HTML
\citep{yang2020html}, MAEC \citep{li2020maec}, KeFVP \citep{niu2023kefvp}, and ECC
Analyzer \citep{cao2024ecc} claims that multimodal models over this data predict
post-call stock volatility better than classical methods.

Two recent observations cast doubt on how much of that progress is real. First,
\citet{scss2024} (``Same Company, Same Signal'') show that transcript
representations used across this literature predominantly encode \emph{company
identity} rather than content: same-ticker transcripts cluster tightly, and
training-free baselines built on a company's own past volatility beat all
transcript-based models on their evaluation. Because volatility is strongly
autocorrelated and company-specific, a model that learns ``which company is this''
inherits most of the apparent skill. Second, a 2025 survey of financial NLP
\citep{finnlp2025survey} finds that only $\sim$14\% of reported results reproduce
exactly, attributing the gap to dead data links, API drift, and contamination.
Together these suggest that the field's leaderboard may be partly an artifact of
identity leakage, weak baselines, and irreproducibility.

This paper reworks an abandoned 2024 study in this lineage from the ground up,
with three goals. (i)~\textbf{Modernise:} replace 2019-era components
(GloVe, Praat-only acoustics, hand-rolled hierarchical transformers) with current
open-weight models---financial sentence embeddings, FinBERT, self-supervised
speech and prosodic features, and instruction-tuned LLMs with constrained
decoding. (ii)~\textbf{Open \& reproduce:} use only openly licensed data and
open-weight models, pin the environment, and release everything needed to rebuild
the study, designing explicitly against the reproducibility crisis. (iii)~\textbf{
Evaluate honestly:} measure every model against strong econometric baselines under
identity-aware controls and leakage-proof splits, so that any positive claim is
attributable to content rather than identity.

Concretely, we ask four research questions:
\begin{description}
  \item[RQ1] Does earnings-call \emph{content} (text and/or audio) add predictive
    signal for post-call volatility beyond past-volatility persistence (HAR-RV,
    GARCH)?
  \item[RQ2] Is multimodal (audio $+$ text) better than the best unimodal model,
    after controlling for past volatility?
  \item[RQ3] Do LLM-extracted \emph{structured, auditable} features (guidance,
    hedging, evasiveness, \dots) outperform opaque dense embeddings?
  \item[RQ4] Do any positive results survive (a) ticker-identity controls,
    (b)~\tickerdisjoint{} splits, and (c) evaluation on post-LLM-knowledge-cutoff
    calls?
\end{description}

The study is pre-registered so that no single outcome strands the work: a clean
negative or mixed answer to RQ1/RQ4 is itself a publishable contribution. The
paper's framing is decided by the data at a pre-registered gate
(\S\ref{sec:discussion}), not retro-fitted to it; this draft is written
\emph{framing-neutral} while the audio, fusion, LLM, and lookahead experiments
are completed.

\paragraph{Contributions.}
\begin{enumerate}
  \item \textbf{\ecvol, an open multimodal volatility benchmark} over
    FinCall-Surprise (primary) and MAEC (secondary): three target families (level
    $v$, change \dv, HAR-residual), temporal and \tickerdisjoint{} splits with a
    30-trading-day embargo, SHA-256 data manifests, and a reproducible harness.
  \item \textbf{Honest baselines everywhere}: persistence, EWMA, HAR-RV,
    GARCH(1,1), and ticker-fixed-effect models reported for every horizon, split,
    and target variant---the comparison most prior work omits.
  \item \textbf{A modern open-model feature ladder on consumer hardware}:
    financial embeddings, FinBERT, WavLM / emotion2vec+ / eGeMAPS audio features,
    fusion heads, and LLM-extracted structured features---all runnable on a single
    16--24\,GB GPU.
  \item \textbf{A diagnostic suite} for this task family: identity probes,
    transcript-shuffle controls, \tickerdisjoint{} evaluation, lookahead-bias tests
    on post-cutoff data, and a gender-confound analysis.
\end{enumerate}
