\section{Related Work}
\label{sec:related}

\paragraph{The benchmark lineage.}
\citet{qin2019what} introduced text$+$audio volatility prediction and the 572-call
EarningsCall dataset, establishing the 3/7/15/30-trading-day log-realised-volatility
target family that the field still uses. MAEC \citep{li2020maec} scaled this to
$\sim$3{,}443 sentence-aligned multimodal calls over the S\&P~1500. HTML
\citep{yang2020html} introduced a hierarchical transformer with multi-task learning
across horizons; VolTAGE \citep{sawhney2020voltage} added graph convolution over
inter-stock relations with text/audio fusion; DialogueGAT \citep{sang2022dialoguegat}
modelled speaker/dialogue structure with graph attention. KeFVP
\citep{niu2023kefvp} combined knowledge-enhanced pre-training with a price-conditioned
time-series module and is the standard SOTA reference. More recent work moves toward
LLMs: ECC Analyzer \citep{cao2024ecc} uses hierarchical LLM summarisation with a RAG
``question bank'' and wav2vec2 features; RiskLabs \citep{cao2024risklabs} fuses calls
with news and market series; AT-FinGPT \citep{atfingpt2025} is an audio-text LLM.
Numeral-aware variants (NumHTML \citep{yang2022numhtml}, NAM/ECNum
\citep{chen2021nam}, GNAVol \citep{shi2023gnavol}) and Q\&A-structure models
\citep{ye2020mraqa} target specific aspects of call language.

\paragraph{Audio and prosody.}
\citet{soundofrisk2024} report that physics-informed acoustic features explain up to
43.8\% of 30-day realised-volatility variance, motivating an audio ladder; the
FinAudio benchmark \citep{cao2025finaudio} cautions that audio-LLMs struggle on long
financial audio, informing our preference for frozen pooled features over end-to-end
audio-LLMs in v1.

\paragraph{Known pitfalls (the methodological core).}
Our design is organised around four documented failure modes.
\emph{(1) Ticker-identity leakage} \citep{scss2024} is the central threat to
validity (\S\ref{sec:intro}); we respond with identity-robust targets (\dv,
HAR-residual), a ticker-fixed-effect baseline, and an identity-control suite
(\S\ref{sec:experiments}). \emph{(2) LLM lookahead bias} \citep{lookahead2024,
datedgpt2025}: a 2024-cutoff model ``predicting'' 2019--2021 outcomes it has
effectively seen; we respond with a planned post-cutoff test set and a
prompt-masking ablation. \emph{(3) Weak baselines}: much prior work omits
persistence, GARCH(1,1), and HAR-RV \citep{corsi2009har}, which are hard to beat at
long horizons; we compute these first and use persistence as the denominator of our
headline metric \citep{gukellyxiu2020}. \emph{(4) Gender bias in audio features}
\citep{ama2024,emobias2024,docfin2022}: we analyse and report a gender confound
rather than debias. We deliberately exclude agentic trading systems and time-series
foundation models from v1 scope.
