\section{Data}
\label{sec:data}

\subsection{Corpora}
We build on two openly licensed multimodal earnings-call corpora and reserve a
third, fresh corpus for a lookahead test.

\textbf{FinCall-Surprise} \citep{fincall2024} (primary; Apache-2.0) contains 2{,}688
calls spanning 2019--2021 with full MP3 audio, JSON transcripts, and slides.
\textbf{MAEC} \citep{li2020maec} (secondary; CC-BY-SA-4.0) contains $\sim$3{,}443
calls over 2015--2018 (S\&P~1500) with sentence-aligned audio features and
transcripts but no raw audio. A fresh \textbf{2025--2026 post-cutoff corpus}
($\geq$200 calls) is acquired by released scripts for the lookahead experiment
(\S\ref{sec:experiments}); raw audio/transcripts from sources with unclear licenses
are never redistributed (a \emph{scripts-not-data} policy).

FinCall-Surprise ships without ticker/date metadata, which we reconstruct from
transcript content and cross-check against price data; identity reconstruction
resolves 2{,}496/2{,}688 earnings calls (92.9\%) and passes a 60/60 manual audit.

\subsection{Price data and targets}
Daily adjusted-close OHLCV is obtained from a free, no-account source and
cross-checked against Tiingo on a random ticker sample (adjusted-return correlation
$>0.999$); delisted or unmatched tickers produce an explicit coverage report rather
than being silently dropped. After price joining, FinCall-Surprise yields 2{,}424
calls with at least one target (97.1\% join rate) and MAEC yields 2{,}578 (75.4\%; a
documented shortfall driven by 2015--2018 delistings), for a combined modelling set
of 5{,}002 calls.

For each call we define returns $r_t = (P_t - P_{t-1})/P_{t-1}$ relative to day
$t=0$, the last trading day before the call's information is public. Because $<$4\%
of calls carry usable timestamps, we apply an after-hours rule (calls assumed to
occur after market close; $t{=}1$ is the next trading session) and flag it.
The primary target is log realised volatility over horizon
$\tau \in \{3,7,15,30\}$ trading days,
\begin{equation}
  v_{\mathrm{post}}(\tau) = \ln\!\Big(\sqrt{\tfrac{1}{\tau}\textstyle\sum_{t=1}^{\tau}(r_t-\bar r)^2}\Big),
\end{equation}
with pre-call volatility $v_{\mathrm{pre}}(\tau)$ defined over the $\tau$ sessions
ending at day~0. We add two identity-robust variants: the \textbf{change}
$\Delta v(\tau) = v_{\mathrm{post}}(\tau) - v_{\mathrm{pre}}(\tau)$, which subtracts
the company's own level, and the \textbf{HAR-residual}
$v_{\mathrm{post}}(\tau) - \widehat{\mathrm{HAR}}(\tau)$, deviation from a train-only
HAR-RV \citep{corsi2009har} forecast. Insufficient post-call history and
zero-variance windows yield \texttt{NaN} targets excluded with a reason code.

\subsection{Leakage-proof splits}
\label{sec:splits}
Three split families are generated once as committed CSVs and guarded by
leakage assertions in CI. \emph{Temporal}: train $<$ validation $<$ test in strict
calendar order ($\sim$70/10/20) with a \textbf{30-trading-day embargo} between
segments so that no 30-day target window crosses a boundary---a constraint most
prior work ignores. \emph{Ticker-disjoint}: companies in validation/test never
appear in training (grouped, seeded), the headline identity-control split.
\emph{Combined}: both constraints simultaneously, reported as the hardest
robustness row. An information rule is codified and enforced: every feature function
receives an \texttt{as\_of} timestamp, and the harness fails any feature that reads
price data after it. FinCall-Surprise spans COVID; per-year breakdowns are
mandatory and a Feb--Apr~2020 exclusion is reported as an exploratory sensitivity.
