\section{Results}
\label{sec:results}

We report results factually and defer the headline framing to
\S\ref{sec:discussion}. Curated headline tables appear here on the identity-robust
\dv{} target for FinCall-Surprise; the complete grid (both corpora, level-$v$ and
\dv, \Rtwo{} and MSE, all splits and horizons) is in
Appendix~\ref{app:complete}. Stars denote Diebold--Mariano significance
($p<0.05$): in Table~\ref{tab:baselines} vs.\ persistence, and in
Table~\ref{tab:text} vs.\ the Stage-1 ticker-FE GBDT.

\subsection{Baselines (Stages 0--1)}
Table~\ref{tab:baselines} shows the econometric floor. HAR-RV is strong at short and
medium horizons on both splits, confirming RQ1's premise that past-volatility
baselines are hard to beat. The one striking failure is the FinCall \emph{temporal}
split at $\tau{=}30$, where every model falls below persistence (HAR-RV
$\Rtwo=-0.287$): the training window is COVID-inflated (Feb--May~2020) while the
test window is calm late~2021, so a long-horizon level forecast trained on the
crisis regime is mis-calibrated. The same models pass comfortably on the
\tickerdisjoint{} split (HAR-RV $\Rtwo=+0.229$ at $\tau{=}30$) and on MAEC, so we
treat this as a documented regime exception rather than a target bug; per-year
breakdowns are mandatory in the appendix.

\input{tables/baselines}

\subsection{Text content (Stage 2)}
Table~\ref{tab:text} shows frozen-text heads against the Stage-1 baseline on \dv.
The result is a clean negative: \emph{text content does not cleanly beat the
identity/past-volatility baselines}. On the FinCall temporal split the text ridge
head is near zero and collapses at $\tau{=}30$; the MLP heads overfit badly. On the
\tickerdisjoint{} split the text ridge head is weak ($\Rtwo$ between $-0.04$ and
$+0.17$) while the past-vol-only head is consistently strong
($\Rtwo\approx0.19$--$0.45$), so any apparent text gain is not separable from what
past volatility already provides. MAEC shows the same pattern at smaller magnitude
(Appendix~\ref{app:complete}).

\input{tables/text}

\subsection{Identity controls (Stage 2 diagnostic)}
Table~\ref{tab:controls} explains the negative result. A linear probe recovers the
ticker from frozen call embeddings at 89.5\% on FinCall (319$\times$ chance) and
53.9\% on MAEC (487$\times$ chance): identity is heavily encoded. The transcript
shuffle is decisive---replacing each test call's transcript with a \emph{different
call from the same ticker} barely changes \Rtwo, whereas a global shuffle degrades
it. The heads are reading \emph{which company} is speaking, not \emph{what} is said.
This is the in-corpus confirmation of \citet{scss2024} and the reason RQ4 is central.

\subsection{Audio, fusion, LLM, and lookahead (pending)}
\pending{Stage 3 audio (Result Table~3): WavLM-Large and emotion2vec+ full-corpus
extraction and heads; eGeMAPS (88-d) already extracted for all 2{,}671 calls.}
\pending{Stage 4 fusion (Result Table~4): the main \S\ref{sec:experiments} ablation
grid.}
\pending{Stage 5 LLM structured features (Result Table~5) and the masking ablation.}
\pending{Phase 7 post-cutoff lookahead evaluation on 2025--2026 calls.}
Each lands as its phase completes; the framing gate (\S\ref{sec:discussion}) is
re-evaluated when the audio results are in.
